Twisted 11-dimensional supergravity, I

### 2021-08-26 draft.tex
mege

The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0^{hol}(X)$.
In fact, we can form the complex 
\beqn\label{eqn:cplx1}
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
\end{tikzcd}
\eeqn
The $\dbar$ operator, as always, is left implicit. 
By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect^{hol}_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.

@@

>>>>

The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
In fact, we can form the complex 
\beqn\label{eqn:cplx1}
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
\end{tikzcd}
\eeqn
The $\dbar$ operator, as always, is left implicit. 
By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.

@@

We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.

The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
\[
E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
\]
whose elements we continue to denote by $\mu$. 
The odd piece is the module 
\[
E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
\]
whose elements we denote by $\alpha$. 
Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
\beqn\label{eqn:e510}
[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
\eeqn
One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.

To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
It is this dense sub super Lie algebra which is simple.

In this short section, we prove the following.

\begin{thm}\label{thm:global}
Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$. 
\end{thm}

On $\CC^5 \times \RR$ the solutions to the linearized equations of motion of the 11-dimensional theory consists of the space of fields $(\mu, [\gamma], b)$ where:
\begin{itemize}
\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
\[
\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
\]
Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
\[
[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
\]
\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
This element is also a ghost in the $\ZZ/2$-graded theory. 
\end{itemize}

If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
This is the algebra of gauge symmetries, or global symmetry algebra, of the theory. 
In the $\ZZ/2$ graded world, the parity shifted object $\Pi \cE$ has the structure of a super Lie algebra.

Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
Equivalently, this is encoded by the full BV action of the 11-dimensional theory. 
After applying the equations of motion this $L_\infty$ structure becomes a (strict) super Lie algebra which we now explicitly describe.

After parity shifted, we've identified the solutions to the linear equations of motion with pairs
\[
(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \Pi \CC .
\]
The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
The elements $b$ are central.

The final term in the BV action $\int \gamma \del \gamma \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
\beqn\label{eqn:eqb}
\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
\eeqn
Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.

We complete the proof of Theorem \ref{thm:global}. 
The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.

On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
In other words, there is an isomorphism
\[
\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
\]
induced by the holomorphic de Rham differential.
This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and 11-dimensional supergravity. 
This completes the proof.

%\begin{proof}
%We define the map directly. 
%The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
%We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory. 
%
%The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
%To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
%We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
%\[
%(H \alpha) (z) = \int_{0}^z \alpha .
%\]
%Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
%We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$. 
%
%All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
%The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
%We will do this in coordinates. 
%Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
%On one hand, in $E(5,10)$ we have 
%\[
%[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
%\]
%
%On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
%\begin{align*}
%[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
%& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
%\end{align*}
%as desired. 
%
%The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
%In $E(5,10)$ we have
%\[
%[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
%\]
%This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
%On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
%\begin{align*}
%[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
%& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
%& = f_i g^{il} \d z_l + \del - \text{exact} .
%\end{align*}
%
%
%\end{proof}
